Additional analysis

### 2018-06-25 03_additional-analysis.Rmd
Better CONSORT saving

```{r build-consort, results="hide", fig.width=10, fig.height=6}
consort <- readRDS(file.path(here(), "data", "completion_summary.rds")) %>% 
  spread(reason, n) %>% 
  mutate(group = 1:n(),
         assigned = Approved + `Failed first attention check`,
         issue = str_replace_all(issue, "assistance", "assist.")) %>% 
  mutate(assigned_label = glue("Allocated to Group {group}\n{crackdown}\n{issue}\n{funding} funding\n\nN = {assigned}"),
         completed_label = glue("Completed\nN = {Approved}\n\n{`Failed first attention check`} failed\nattention check"))

@@

# Connect boxes
grid.newpage()
total; randomized; ineligible
connectGrob(total, randomized, "v")
connectGrob(total, ineligible, "-")

group1; group2; group3; group4; group5; group6; group7; group8
connectGrob(randomized, group1, "N")
connectGrob(randomized, group2, "N")
connectGrob(randomized, group3, "N")
connectGrob(randomized, group4, "N")
connectGrob(randomized, group5, "N")
connectGrob(randomized, group6, "N")
connectGrob(randomized, group7, "N")
connectGrob(randomized, group8, "N")

group1_completed; group2_completed; group3_completed; group4_completed; 
group5_completed; group6_completed; group7_completed; group8_completed
connectGrob(group1, group1_completed, "N")
connectGrob(group2, group2_completed, "N")
connectGrob(group3, group3_completed, "N")
connectGrob(group4, group4_completed, "N")
connectGrob(group5, group5_completed, "N")
connectGrob(group6, group6_completed, "N")
connectGrob(group7, group7_completed, "N")
connectGrob(group8, group8_completed, "N")

# Use a global plot device temporarily because each chunk starts a new viewport
# and I want to use grid.grab() on this chunk, but I also want to hide the
# output from grid.grab() since knitr/grid inexplicably insist on plotting a
# second figure even when wrapping grid.grab() in invisible() or enabling
# results="hide" in the chunk options. So, the hacky solution here is to use a
# global device, capture the grid output in a new chunk that isn't included, and
# turn off the global plot device later. I also include code that isn't run for
# the sake of readability (i.e. fig_consort would come out of nowhere otherwise)
#
# See https://stackoverflow.com/a/17509770/120898
knitr::opts_knit$set(global.device = TRUE)
```

```{r grab-figure-actual, include=FALSE}
fig_consort <- grid.grab()
```

```{r grab-figure-fake, eval=FALSE}
fig_consort <- grid.grab()
```

```{r show-save-consort, fig.width=10, fig.height=6}
# Turn off global device
knitr::opts_knit$set(global.device = FALSE)

fig_consort %T>%
  ggsave(., filename = file.path(here(), "output", "figures", "consort.pdf"),
         width = 10, height = 6, units = "in", device = cairo_pdf) %>% 
  ggsave(., filename = file.path(here(), "output", "figures", "consort.png"),
         width = 10, height = 6, units = "in", type = "cairo", dpi = 300)
```

>>>>

```{r build-consort}
consort <- readRDS(file.path(here(), "data", "completion_summary.rds")) %>% 
  spread(reason, n) %>% 
  mutate(group = 1:n(),
         assigned = Approved + `Failed first attention check`,
         issue = str_replace_all(issue, "assistance", "assist.")) %>% 
  mutate(assigned_label = glue("Allocated to Group {group}\n{crackdown}\n{issue}\n{funding} funding\n\nN = {assigned}"),
         completed_label = glue("Completed\nN = {Approved}\n\n{`Failed first attention check`} failed\nattention check"))

@@

total_random_connect <- connectGrob(total, randomized, "v")
total_ineligible_connect <- connectGrob(total, ineligible, "-")

rand_connect1 <- connectGrob(randomized, group1, "N")
rand_connect2 <- connectGrob(randomized, group2, "N")
rand_connect3 <- connectGrob(randomized, group3, "N")
rand_connect4 <- connectGrob(randomized, group4, "N")
rand_connect5 <- connectGrob(randomized, group5, "N")
rand_connect6 <- connectGrob(randomized, group6, "N")
rand_connect7 <- connectGrob(randomized, group7, "N")
rand_connect8 <- connectGrob(randomized, group8, "N")

complete_connect1 <- connectGrob(group1, group1_completed, "N")
complete_connect2 <- connectGrob(group2, group2_completed, "N")
complete_connect3 <- connectGrob(group3, group3_completed, "N")
complete_connect4 <- connectGrob(group4, group4_completed, "N")
complete_connect5 <- connectGrob(group5, group5_completed, "N")
complete_connect6 <- connectGrob(group6, group6_completed, "N")
complete_connect7 <- connectGrob(group7, group7_completed, "N")
complete_connect8 <- connectGrob(group8, group8_completed, "N")

full_chart <- list(total, randomized, ineligible, total_random_connect, total_ineligible_connect,
                   group1, group2, group3, group4, group5, group6, group7, group8,
                   rand_connect1, rand_connect2, rand_connect3, rand_connect4, 
                   rand_connect5, rand_connect6, rand_connect7, rand_connect8,
                   group1_completed, group2_completed, group3_completed, group4_completed, 
                   group5_completed, group6_completed, group7_completed, group8_completed,
                   complete_connect1, complete_connect2, complete_connect3, complete_connect4, 
                   complete_connect5, complete_connect6, complete_connect7, complete_connect8) 
```

```{r show-save-consort, fig.width=10, fig.height=6}
# Ordinarily, you can use grid.grab() to save the output of a grid figure into
# an object and then use that in ggsave(). However, when knitting, this creates
# a duplicate plot, which is frustrating. So instead, we use walk() to reprint
# all the grobs within specific pdf and png devices
#
# See https://stackoverflow.com/a/17509770/120898 for a similar issue

# Save as PDF
cairo_pdf(filename = file.path(here(), "output", "figures", "consort.pdf"),
          width = 10, height = 6)
grid.newpage()
walk(full_chart, ~ print(.))
invisible(dev.off())

# Save as PNG
png(filename = file.path(here(), "output", "figures", "consort.png"), 
    width = 10, height = 6, units = "in",
    bg = "white", res = 300, type = "cairo")
grid.newpage()
walk(full_chart, ~ print(.))
invisible(dev.off())

# Show in knitted document
grid.newpage()
walk(full_chart, ~ print(.))
```
